---
title: "Investment Report for Projects in `r params$country`"
author: "Kleyton da Costa"
output: 
  html_document:
    css: "styles.css"
    toc: true
    toc_float: true
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  country: Brazil
  year_start: 2017-07-01
  year_end: 2018-06-30
  fy: 2018
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'left', echo = FALSE)
```

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(ggthemes)

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")

investment_region_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/52f5414f6504e0503e86eb1043afa9b3d157fab2/investment_region_summary.csv")

investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")
```


# Datasets 

## Investment Annual Summary
The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.

1. East Asia and the Pacific      
2. Europe and Central Asia        
3. Latin America and the Caribbean
4. Middle East and North Africa   
5. South Asia                     
6. Sub-Saharan Africa


```{r investment-annual-summary, out.width='70%'}
ggplot(investment_annual_summary, aes(x = fiscal_year, y = dollars_in_millions, color = region)) +
  geom_line() +
  labs(
    title = "",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )+
  theme_fivethirtyeight()+
  theme(plot.background = element_rect(fill = "#F5F5F5"),
        legend.background = element_rect(fill = "#F5F5F5"))
```

```{r tables}
kable(investment_region_summary, col.names = c('Region','Dollars in Millions'), align = c('c','c'), caption = "Table 1.1 The total investment summary for each region for the 2012 to 2018 fiscal years.")
```

## Investment Projects in `r params$country`

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts. Projects that do not have an associated investment amount are excluded from the plot.

```{r country-investment-projects, out.width='70%', warning=FALSE}
country_investment_projects <- investment_services_projects %>%
  filter(country == params$country) 

ggplot(country_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )+
  theme_fivethirtyeight()+
  theme(plot.background = element_rect(fill = "#F5F5F5"),
        legend.background = element_rect(fill = "#F5F5F5"))
```

## Investment Projects in `r params$country` in `r params$fy`
The `investment_services_projects` dataset was filtered below to focus on information about each investment project from the `r params$fy` fiscal year, and is referred to as `country_annual_investment_projects`. Projects that do not have an associated investment amount are excluded from the plot.

```{r country-annual-investment-projects,out.width='70%', warning=FALSE}
country_annual_investment_projects <- investment_services_projects %>%
  filter(country == params$country,
         date_disclosed >= params$year_start,
         date_disclosed <= params$year_end) 

ggplot(country_annual_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  labs(
    title = "",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  ) +
  theme_fivethirtyeight()+
  theme(plot.background = element_rect(fill = "#F5F5F5"),
        legend.background = element_rect(fill = "#F5F5F5"))
```



